H~5~: Organizational practices

### 2023-10-26 notebook/results-practices.qmd
Add accountability across government relationship

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \right) \bigr]
\end{aligned}
$$
```{r h5a-calc-estimands}
h5a_mms <- preds_all %>% 
  group_by(feat_transp_short, .draw) %>% 
  summarize(avg = mean(.epred))

h5a_amces <- h5a_mms %>% 
  group_by(feat_transp_short) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
```

```{r plot-h5a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset-right
p_h5a_mms <- h5a_mms %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

@@

# H~5b~: Relationship with host government, organizational practices

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices

@@

>>>>

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \right) \bigr]
\end{aligned}
$$
```{r h5a-calc-estimands}
h5a_mms <- preds_all %>% 
  group_by(feat_acc, .draw) %>% 
  summarize(avg = mean(.epred))

h5a_amces <- h5a_mms %>% 
  group_by(feat_transp) %>% 
  compare_levels(variable = avg, by = feat_transp, comparison = "control")
```

```{r plot-h5a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset-right
p_h5a_mms <- h5a_mms %>% 
  ggplot(aes(x = avg, y = feat_acc, fill = feat_acc)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

@@

# H~5b~: Relationship with host government and organizational practices

## Transparency

::: {.callout-tip icon=false}
### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices

@@

## Accountability

::: {.callout-tip icon=false}
### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b2~: Relationship with host government, organizational practices

**Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are accountable and hold regular third party audits**
:::

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Accountability} = \text{Yes} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Accountability} = \text{Yes} \mid \text{Relationship = Friendly} \right) \bigr]
\end{aligned}
$$

```{r h5b2-calc-estimands}
h5b2_mms <- preds_all %>% 
  group_by(feat_acc_short, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

h5b2_amces <- h5b2_mms %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_acc_short, comparison = "control")
```

```{r plot-h5b2-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5b2_mms <- h5b2_mms %>% 
  ggplot(aes(x = avg, y = feat_acc_short, fill = feat_acc_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(9, 4)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )

p_h5b2_amces <- h5b2_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_acc_short,
    delim = " - ", 
    names = c("feat_acc_short", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_acc_short = "No", feat_govt = "Friendly relationship with government") %>%
  add_row(avg = 0, feat_acc_short = "No", feat_govt = "Criticized by government") %>%
  add_row(avg = 0, feat_acc_short = "No", feat_govt = "Under government crackdown") %>%
  mutate(feat_acc_short = factor(feat_acc_short, levels = levels(h5b2_mms$feat_acc_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5b2_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_acc_short, fill = feat_acc_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(9, 4)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h5b2_mms | p_h5b2_amces
```

```{r table-h5b2-mm-amce}
#| column: body-outset-right
h5b2_tbl_mm <- h5b2_mms %>% 
  group_by(feat_govt, feat_acc_short) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_govt), desc(feat_acc_short)) %>% 
  select(feat_acc_short, feat_govt, nice)

h5b2_tbl_amces <- h5b2_amces %>% 
  group_by(feat_govt, feat_acc_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  ungroup() %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_acc_short, diff_nice = nice, p_neq_0)

bind_cols(
  h5b2_tbl_mm, 
  h5b2_tbl_amces %>% 
    add_row(contrast = NA, .after = 1) %>% 
    add_row(contrast = NA, .after = 3) %>% 
    add_row(contrast = NA, .after = 5)
) %>% 
  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
  group_by(feat_govt) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_acc_short, contrast)) %>% 
  cols_label(
    feat_acc_short = "Accountability", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    diff_nice = "Posterior ∆",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_fill(color = "grey90"),
    locations = cells_row_groups()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, diff_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```
